Calculating Entropies With Nested Sampling

### 2017-02-04 paper/ms.tex
Working on the appendix

The central issue about the value of a parameter $\x$ asks
``what is the value of $\x$, precisely?''. However, in practice we often
don't need or want to know $\x$ to arbitrary precision. Using the central
issue can also lead to counterintuitive results if you don't keep its
definition in mind. For example, suppose $\x$ could take any integer value
from 1 to 1 billion. If we learned that the last digit of $\x$ was a 9, we
will have ruled out nine tenths of the possibilities, and therefore obtained
a lot of information about the central issue. However, in many applications
this ``information'' would be basically useless.

The reason is that we often want to ask a slightly different question.
For example, suppose we want to know the value of $\x$ to within a tolerance
of $\pm 5$. The following statements would resolve the issue:
\begin{itemize}
\item $\x \in \{1, ..., 10\}$ and anything that implies it
\item $\x \in \{2, ..., 11\}$ and anything that implies it
...
\end{itemize}

>>>>

The central issue about the value of a parameter $\x$ asks
``what is the value of $\x$, precisely?''. However, in practice we often
don't need or want to know $\x$ to arbitrary precision. Using the central
issue can also lead to counterintuitive results if you don't keep its
definition in mind. For example, suppose $\x$ could take any integer value
from 1 to 1 billion. If we learned the last digit of $\x$, we
will have ruled out nine tenths of the possibilities, and therefore obtained
a lot of information about the central issue. However,
this information might be useless {\em for practical purposes}.
If we learned the final
digit was a 9, $\x$ could still be 9, or 19, or 29, any number ending in 9
up to 999,999,999.

In practice, we may
want to ask a question that is different from the central issue.
For example, suppose we want to know the value of $\x$ to within a tolerance
of $\pm 5$. Any of the following statements would resolve the issue:
\begin{itemize}
\item $\x \in \{1, ..., 11\}$ and anything that implies it
\item $\x \in \{2, ..., 12\}$ and anything that implies it
\item $\x \in \{3, ..., 13\}$ and anything that implies it\\
...
\item $\x \in \{999,999,990, ..., 1,000,000,000\}$ and anything that implies it.
\end{itemize}
